The one characterizing the parental care stages

### 2019-10-18 docs/ms1-charactization.Rmd
updated ms

---
title: "The one characterizing the parental care stages"
output: md_document
author:
- Principal Investigators - Rebecca Calisi, Matt MacManes, John Wingfield
- Postdocs - Suzanne Austin, Rayna Harris, Jesse Krause, 
- Grad students - Victoria Farrar, April Booth, Andrew Lang
- Undergrads - Tanner Feustel, Candice Lee, Annie Bond?
- Others - Fred?, Rechelle Viernes
---

@@

## Figure 3: PCA

_Needs to be replaced with a better PCA plot showing all samples as points_

![](../figures/pca/pca-1.png)

>>>>

---
title: "The one characterizing the parental care stages"
output: md_document
author:
- PIs - Rebecca Calisi, Matt MacManes
- Postdocs - Suzanne Austin, Rayna Harris, Jesse Krause
- Grad students - Victoria Farrar, April Booth, Andrew Lang
- Staff - Rechelle Viernes
---

@@

## Figure 3: PCA + tSNE

![](../figures/pca/pca-3.png)

![](../figures/pca/tSNE-2.png)
